
### {{plot_title}}

<!-- Page created on {{ date }} -->
```{r}
{{ env_id }} = readRDS("envs/{{ env_id }}.rds")

plotly::plotlyOutput("plot_{{ env_id }}")
output$plot_{{ env_id }} <- plotly::renderPlotly({

  if (!{{ env_id }}$x_selection){
    x_value <- {{ env_id }}$x[[1]]
    x_title <- names({{ env_id }}$x)
  } else {
    x_value <- {{ env_id }}$x[[input$select_x_{{ env_id }}]]
    x_title <- input$select_x_{{ env_id }}
  }

  if (!{{ env_id }}$y_selection){
    y_value <- {{ env_id }}$y[[1]]
    y_title <- names({{ env_id }}$y)
  } else {
    y_value <- {{ env_id }}$y[[input$select_y_{{ env_id }}]]
    y_title <- input$select_y_{{ env_id }}
  }

  p <- plotly::plot_ly(data.frame(x_value, y_value),
               x = x_value,
               y = y_value,
               split = x_value,
               type = 'violin',
               box = list(
                 visible = T
                 ),
               meanline = list(
                 visible = T
                 )
               )
p <- plotly::layout(p,
                    xaxis = list(title = x_title),
                    yaxis = list(title = y_title,
                                 zeroline = F))

p
})
```

***

```{r}
# selection field for x
if ({{ env_id }}$x_selection){
  selectInput("select_x_{{ env_id }}", label = "Select data for x axis:",
            choices = names({{ env_id }}$x))
}

# selection field for y
if ({{ env_id }}$y_selection){
  selectInput("select_y_{{ env_id }}", label = "Select data for y axis:",
            choices = names({{ env_id }}$y))
}
```

Plot description:

Sequencing is called *saturated* when generating more sequencing output from a cDNA library does not substantially increase the number of detected features in a sample. Since the number of detected features can act as a technical confounder, and thereby drive substructure in the data, it is advisable to aim for a saturated sequencing by either adding more sequencing output or decreasing the number of samples until saturation is achieved. [@zhang_one_2018] gives advise on how to choose the optimal cell number given a fixed sequencing budget

